Constrained, yet diverse: Phylogenetic and morphological filtering in epiphytic ferns

### 2019-08-08 ms/manuscript.Rmd
Use :: for here::

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, cache = TRUE)
library(drake)
library(gt)
library(patchwork)
library(knitr)
library(kableExtra)
library(here)
library(magrittr)
library(scales)
library(tidyverse)
library(conflicted)

@@

# Read in csv version of the table
traits_used <- read_csv(here("data/table_1.csv"))

@@

# Write out table in rich text format
phylosig_cont_traits_table %>%
  gt(rowname_col = "trait") %>%
  cols_label(
    kval = md("*K*"),
    k_pval = md("*P*(*K*)"),
    lambda_pval = md("*P*(lambda)"),
    lambda = "lambda"
  )  %>% 
  as_rtf() %>%
  write_lines(here("ms/table2.rtf"))

@@

# Write out table in rich text format
phylosig_binary_traits_table %>%
  gt(rowname_col = "trait") %>%
  cols_label(
    num_present = "Number of presences",
    num_absent = "Number of absences",
    D = md("*D*"),
    prob_random = md("*P*(rnd)"),
    prob_brownian = md("*P*(bm)")
  ) %>% 
  as_rtf() %>%
  write_lines(here("ms/table3.rtf"))

@@

# Write out table in rich text format
pic_table %>%
gt(rowname_col = "trait") %>%
  cols_label(
    n_contrasts = "Num. constrasts",
    n_pos_con = "Num. pos. constrasts",
    statistic = md("*t*"),
    p.value = md("*P*"),
  ) %>% 
  as_rtf() %>%
  write_lines(here("ms/table4.rtf"))

@@

# Write out table in rich text format
correlated_evo_test_table %>%
gt(rowname_col = "trait") %>%
  cols_label(
    logL_indep = "LogL(independent)",
    logL_dep = "LogL(dependent)",
    likelihood_ratio = "Likelihood ratio",
    pval = md("*P*"),
  ) %>% 
  as_rtf() %>%
  write_lines(here("ms/table5.rtf"))

@@

```{r traits-used-image, fig.width=7, fig.height=7, fig.cap = "Examples of traits used in this study."}
knitr::include_graphics(here("images/Figure_3_1_traits_lowres.pdf"))
```

@@

```{r climate, fig.height = 4, fig.width = 6, fig.cap = "Microclimatic variables."}
climate_plot
```

@@

```{r pca, fig.height = 6, fig.width = 6, fig.cap = "Trait PCA."}
pca_plot
```

@@

```{r tree, fig.height = 8, fig.width = 6, fig.cap = "Traits on tree."}
traits_with_tree
```

@@

```{r heatmap, fig.height = 4, fig.width = 6, fig.cap = "Variable importance scores."}
importance_heatmap
```

@@

```{r cwm-div, fig.height = 4, fig.width = 8, fig.cap = "Community-weighted means."}
combined_cwm_plots
```

@@

```{r comm-div, fig.height = 8, fig.width = 4, fig.cap = "Community diversity metrics."}
combined_comm_div_plots
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, cache = TRUE)
library(drake)
library(gt)
library(patchwork)
library(knitr)
library(kableExtra)
library(magrittr)
library(scales)
library(tidyverse)
library(conflicted)

@@

# Read in csv version of the table
traits_used <- read_csv(here::here("data/table_1.csv"))

@@

# Write out table in rich text format
phylosig_cont_traits_table %>%
  gt(rowname_col = "trait") %>%
  cols_label(
    kval = md("*K*"),
    k_pval = md("*P*(*K*)"),
    lambda_pval = md("*P*(lambda)"),
    lambda = "lambda"
  )  %>% 
  as_rtf() %>%
  write_lines(here::here("ms/table2.rtf"))

@@

# Write out table in rich text format
phylosig_binary_traits_table %>%
  gt(rowname_col = "trait") %>%
  cols_label(
    num_present = "Number of presences",
    num_absent = "Number of absences",
    D = md("*D*"),
    prob_random = md("*P*(rnd)"),
    prob_brownian = md("*P*(bm)")
  ) %>% 
  as_rtf() %>%
  write_lines(here::here("ms/table3.rtf"))

@@

# Write out table in rich text format
pic_table %>%
gt(rowname_col = "trait") %>%
  cols_label(
    n_contrasts = "Num. constrasts",
    n_pos_con = "Num. pos. constrasts",
    statistic = md("*t*"),
    p.value = md("*P*"),
  ) %>% 
  as_rtf() %>%
  write_lines(here::here("ms/table4.rtf"))

@@

# Write out table in rich text format
correlated_evo_test_table %>%
gt(rowname_col = "trait") %>%
  cols_label(
    logL_indep = "LogL(independent)",
    logL_dep = "LogL(dependent)",
    likelihood_ratio = "Likelihood ratio",
    pval = md("*P*"),
  ) %>% 
  as_rtf() %>%
  write_lines(here::here("ms/table5.rtf"))

@@

```{r traits-used-image, fig.width=7, fig.height=7, fig.cap = "Examples of traits used in this study."}
knitr::include_graphics(here::here("images/Figure_3_1_traits_lowres.pdf"))
```

@@

```{r climate, fig.height = 4, fig.width = 6, fig.cap = "Microclimatic variables."}
climate_plot
ggsave(plot = climate_plot, filename = here::here("ms/fig1.tiff"), height = 4, width = 6, units = "in", dpi = "retina")
```

@@

```{r pca, fig.height = 6, fig.width = 6, fig.cap = "Trait PCA."}
pca_plot
ggsave(plot = pca_plot, filename = here::here("ms/fig2.tiff"), height = 6, width = 6, units = "in", dpi = "retina")
```

@@

```{r tree, fig.height = 8, fig.width = 6, fig.cap = "Traits on tree."}
traits_with_tree
ggsave(plot = traits_with_tree, filename = here::here("ms/fig3.tiff"), height = 8, width = 6, units = "in", dpi = "retina")
```

@@

```{r heatmap, fig.height = 4, fig.width = 6, fig.cap = "Variable importance scores."}
importance_heatmap
ggsave(plot = importance_heatmap, filename = here::here("ms/fig4.tiff"), height = 4, width = 6, units = "in", dpi = "retina")
```

@@

```{r cwm-div, fig.height = 4, fig.width = 8, fig.cap = "Community-weighted means."}
combined_cwm_plots
ggsave(plot = combined_cwm_plots, filename = here::here("ms/fig5.tiff"), height = 4, width = 8, units = "in", dpi = "retina")
```

@@

```{r comm-div, fig.height = 8, fig.width = 4, fig.cap = "Community diversity metrics."}
combined_comm_div_plots
ggsave(plot = combined_comm_div_plots, filename = here::here("ms/fig6.tiff"), height = 8, width = 4, units = "in", dpi = "retina")
```
